Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries

### 2019-12-01 public/paper/pyg4ometry.tex
Complete tables

\begin{table}[hbt!]
\centering
\begin{tabular}{| l | l | } \hline
Geant4 solid			& FLUKA constuction			\\ \hline
Box					& XYP, XZP, YZP 				\\
Tube					& ZCC, XYP	 				\\
CutTube				& ZCC, PLA					\\
Cone				& TRC						\\
Para					& ARB						\\
Trd					& ARB						\\
Trap					& ARB						\\
Sphere				& SPH, WED					\\
Orb					& SPH						\\
Torus				& (PLA)						\\
Polycone				& (PLA)						\\
GenericPolycone		& (PLA)						\\
Polyhedra				& (PLA)						\\
Eltube				& ZEC, XYP					\\
Ellipsoid				& ELL						\\
Elcone				& QUA						\\
Paraboloid			& QUA						\\
Hype					& QUA						\\
Tet					& PLA						\\
Xtru					& PLA						\\
TwistedBox			& (PLA)						\\
TwistedTtap			& (PLA)						\\
TwistedTrd			& (PLA)				 		\\
TwistedTube			& (PLA)						\\
Arb8					& ARB						\\
Tessellated			& (PLA)					 	\\
Union				& | zone1 | zone2				\\
Subtraction			& +zone1 -zone2				\\
Intersection			& +zone1 +zone2				\\
MultiUnion			& | zone1 | zone2 | zone3 | ...	\\
ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
\end{tabular}
\end{table}

>>>>

\begin{table}[hbt!]
\centering
\begin{tabular}{| l | l | } \hline
Geant4 solid			& FLUKA constuction			\\ \hline
Box					& XYP, XZP, YZP 				\\
Tube					& ZCC, XYP	 				\\
CutTube				& ZCC, PLA					\\
Cone				& TRC						\\
Para					& ARB						\\
Trd					& ARB						\\
Trap					& ARB						\\
Sphere				& SPH, WED					\\
Orb					& SPH						\\
Torus				& ZCC, PLA					\\
Polycone				& ARB						\\
GenericPolycone		& ARB						\\
Polyhedra				& ARB						\\
Eltube				& ZEC, XYP					\\
Ellipsoid				& ELL						\\
Elcone				& QUA						\\
Paraboloid			& QUA						\\
Hype					& QUA						\\
Tet					& PLA						\\
Xtru					& PLA						\\
TwistedBox			& ARB						\\
TwistedTtap			& ARB						\\
TwistedTrd			& ARB				 		\\
TwistedTube			& ARB						\\
Arb8					& ARB						\\
Tessellated			& N/A					 	\\
Union				& | zone1 | zone2				\\
Subtraction			& +zone1 -zone2				\\
Intersection			& +zone1 +zone2				\\
MultiUnion			& | zone1 | zone2 | zone3 | ...	\\
ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
\end{tabular}
\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
\end{table}
